Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-10-19 main.tex
Fixesing inaccuracies for combinatorial semantics

@@

% category names
\newcommand{\Ecospans}{{\catname{ECsp_{D}(EHyp_{\Sigma})}}}
\newcommand{\MdaEcospans}{{\catname{MAECsp_{D}(EHyp_{\Sigma})}}}
\newcommand{\WellTypedMdaEcospans}{{\catname{\overline{MAECsp_{D}(EHyp_{\Sigma})}}}}

@@

\title{Equivalence Hypergraphs:\\ Semantics of E-Graphs and their Generalization to 
Monoidal Theories}
\author{Chris Barrett, Dan Ghica, Aleksei Tiurin}

@@

\begin{abstract}
Abstract.
\end{abstract}

@@

\subsection*{Acknowledgements}
Sadrzadeh Mehrnoosh

\clearpage
\bibliographystyle{acm}
\bibliography{bibliography}

>>>>

% for quotienting
% \usepackage{faktor}
\usepackage{xfrac}

@@

% category names
\newcommand{\MdaCospans}{{\catname{MACsp_{D}(Hyp_{\Sigma})}}}

\newcommand{\Ecospans}{{\catname{ECsp_{D}(EHyp_{\Sigma})}}}
\newcommand{\MdaEcospans}{{\catname{MAECsp_{D}(EHyp_{\Sigma})}}}
\newcommand{\WellTypedMdaEcospans}{{\catname{\overline{MAECsp_{D}(EHyp_{\Sigma})}}}}

@@

\title{Equivalence Hypergraphs: E-Graphs for Monoidal Theories }
\author{Chris Barrett}
\author{Dan Ghica}
\author{Aleksei Tiurin}

@@

\begin{abstract}
Equivalence graphs (e-graphs), together with a technique called equality saturation, have recently proved a powerful and practical tool for optimization of programs.  We describe a categorical semantics for e-graphs over algebraic theories in terms of Cartesian categories enriched over a semilattice,  and define a natural generalization in terms of symmetric monoidal categories to account for monoidal theories,  with the aim of allowing optimization of a larger class of programs based on string diagrams.  We further develop a sound and complete combinatorial representation of morphisms in our category based on a generalization of hypergraphs,  which we call e-hypergraphs,  which factor out many structural equations.  Finally, we consider the question of efficient rewriting in our setting.
\end{abstract}

@@

\subsection*{Acknowledgements}
We are grateful to Sadrzadeh Mehrnoosh for enlightening discussions on potential applications of e-hypergraphs to computational linguistics.

\bibliographystyle{acm}
\bibliography{bibliography}
